\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-13 Data_csv/Paper/paper.tex
push

\begin{figure}[H]
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering

		\includegraphics[width=4.3cm]{t8_unstained_ppsc1.png}
		\caption{}
		\label{scatter1}

	\end{subfigure}%
	\begin{subfigure}{.22\textwidth}
		\centering

		\includegraphics[width=4.3cm]{t8_stained_ppsc1.png}
		\caption{}
		\label{scatter2}

	\end{subfigure}
	\caption{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
	\label{scatterplot}
\end{figure}	
\vspace{-0.2cm}
On Fig. \ref{scatter1} is a scatter plot of an unstained sample of PPSC. On the vertical axis is represented red fluorescence. The horizontal axis shows green fluorescence. A big black cluster and a red one above it can be observed. The black cluster is composed of SC cells and remaining particles. They show  low red and green fluorescence values. The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.

>>>>

	\begin{minipage}{.48\linewidth}
	%	\hspace{-0.3cm}
	%	\begin{subfigure}{.25\textwidth}
			\centering

			\includegraphics[width=1\linewidth]{t8_unstained_ppsc1.png}
			\captionof{figure}{Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
			\label{scatter1}

	%	\end{subfigure}%
	%	\begin{subfigure}{.22\textwidth}
	\end{minipage}\hspace{.2cm}
	\begin{minipage}{.48\linewidth}

			\centering

			\includegraphics[width=1\linewidth]{t8_stained_ppsc1.png}
			\captionof{figure}{Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
			\label{scatter2}

	%	\end{subfigure}
	%	\caption{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
	%	\label{scatterplot}
	\end{minipage}

On Fig. \ref{scatter1} is a scatter plot of an unstained sample of PPSC. On the vertical axis is represented red fluorescence. The horizontal axis shows green fluorescence. A big black cluster and a red one above it can be observed. The black cluster is composed of SC cells and remaining particles. They show  low red and green fluorescence values. The PP cells express mCherry and therefore show red fluorescence, which causes an upwards shift on the plot, forming the red cluster above.
